%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Work Experience}


%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}
%---------------------------------------------------------        
      \cventry
    {Consultant 2} % Job title
    {Guidewire Software} % Organization
    {Dublin, Ireland} % Location
    {June. 2016 - PRESENT} % Date(s)
    {
    \begin{cvitems} % Description(s) of tasks/responsibilities
    	\item {I have worked primarily as a Functional Consultant at Guidewire. Responsible for implementing  bespoke functionality to help clients better manage their Lines of Business. As well as this, I am also tasked with providing technical product expertise to project stakeholders through Knowledge Transfer Sessions, Code Reviews, Documentation etc. with the aim of ensuring a smooth go-live. }
    	\item {In addition to my work as a Consultant I am also a member of a mentoring program, I assist in the recruitment process through Code Reviews and I am a member of the Social Committee responsible for organizing work events.{\\}}
        \item {\textbf{\footnotesize{Elephant Insurance Upgrade Project}}~~~·~~~{\tiny (Aug. 2016 - Oct. 2017)} {\\}
	~~~·~~~ Upgrading existing Guidewire implementation from Insurance Suite Version 7 - 9. {\\}
	~~~·~~~ Provide guidance to the Client regarding changes between versions.
	{\\}
        }
%---------------------------------------------------------        Germania
    \item {\textbf{\footnotesize{Germania Insurance Implementation Project}}~~~·~~~{\tiny (Aug. 2016 - Oct. 2017)}{\\}
	~~~·~~~Large Scale Scrum Agile Project. Responsible for the Personal Auto Line of Business.
{\\}
	~~~·~~~Developed a custom Business Rules Engine to alert relevant Business Stakeholders if particular conditions are met in a business transaction.
{\\}
	~~~·~~~Configured Personal Auto Line to consume external vendor services to provide VIN Info, Credit Score, Vehicle Records and Claims History.  
{\\}
	~~~·~~~Worked in conjunction with several other teams to provide support and resolve dependencies. 
{\\}
{\\}
	{\textbf{Primary Technologies Used:}} Java, Gosu, Git, SVN, Jenkins, SOAP, WSDL, JMS, SQL, Jetty, Tomcat.}
      \end{cvitems}
    }
%---------------------------------------------------------
  \cventry
    {Junior Office Administrator} % Job title
    {National Treasury Management Agency (NTMA)} % Organization
    {Dublin Ireland} % Location
    {Dec. 2015 - Feb. 2016} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Joined on a temporary basis to assist compliance to Government initiative related to the Data Protection Act.}
        \item {Main duty involved re-categorizing documents entered in error to the National Incident Management System (NIMs).}
        \item {Other Duties: {\\}~~~·~~~Database entry /reporting.{\\}~~~·~~~Physical records management{\\}~~~·~~~General office support tasks. }
      \end{cvitems}
    }
%---------------------------------------------------------
\end{cventries}
