%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Work Experience}
%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}
%---------------------------------------------------------        
   \cventry
    {Software Consultant 2} % Job title
    {Guidewire Software} % Organization
    {Dublin, Ireland} % Location
    {June. 2016 - PRESENT} % Date(s)
    {
    \begin{cvitems} % Description(s) of tasks/responsibilities
     	\item {Currently a Software Consultant at Guidewire, trained and certified in Policy Center \& Integration best practices.}
     	\item {Provide Product Guidance to Clients through Code Reviews, Knowledge Transfers and Documentation.}
     	\item {Mentor for new hires and Member of the Guidewire Social Committee.{~\vskip 0.05in}}
         %-------------------------------------------------------------------------
         %   Grinnell
         %-------------------------------------------------------------------------
         {\textbf{Grinnell Implemtaion}\hfill\entrydatestyle{(Jul. 2018- PRESENT)}{~\vskip 0.05in}
         \begin{itemize}
          \item {Developing a custom Web Frontend (ES6, Angular, jQuery) for Guidewire's Insurance Suite using AngularJS.}
          \item {Building a Backend JSON-RPC API to integrate frontend with Insurance Suite services.}{~\vskip 0.05in}
        \end{itemize}}
       %-------------------------------------------------------------------------
         %   Elephant 
         %-------------------------------------------------------------------------
       {\textbf{Elephant Upgrade}\hfill\entrydatestyle{(Oct. 2017- Jul. 2018)}{~\vskip 0.05in}
         \begin{itemize}
		       \item {Upgraded Elephant's Insurance Suite implementation from Version 7 - 9.}
		       \item {Responsible for refactoring / rebuilding large sections of client Java/Gosu Code, web-services, external integrations, data model etc.}
		       \item {Developed Backend API to support Frontend development team.}{~\vskip 0.05in}
         \end{itemize}}
         %-------------------------------------------------------------------------
         %   Germania 
         %-------------------------------------------------------------------------
      {\textbf{Germania Implementation}\hfill\entrydatestyle{(Aug. 2016 - Oct. 2017)}{~\vskip 0.05in}{
          \begin{itemize}
            \item {Responsible for functional implementation of Germania's Personal Auto Line of Business, developed Entity Validation framework. }
            \item {Implemented Custom Business Rules Framework configurable by Business at runtime, makes use of Recursion and Java Reflection to build and access a representation of the Customer Data Model. Currently used extensively Germania's in Production environment. }
            {~\\}
          \end{itemize}}
      }      
    \end{cvitems}
    }
  \cventry
    {Junior Office Administrator} % Job title
    {National Treasury Management Agency (NTMA)} % Organization
    {Dublin Ireland} % Location
    {Dec. 2015 - Feb. 2016} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Joined on a temporary basis to assist compliance to Government initiative related to the Data Protection Act.}
        \item {Main duty involved re-categorizing documents entered in error to the National Incident Management System (NIMs).}
        \item {Other Duties:
        	\begin{itemize}
        		\item {Database entry /reporting.}
			    	\item {Physical records management}
				    \item {General office support tasks.}
		    	\end{itemize}
			}
      \end{cvitems}
    }
%---------------------------------------------------------
\end{cventries}
